Technical Report

### 2018-06-18 fully-abstract-comp/technical-report.tex
Removed a TODO that was resolved.
Technical fix: exact equality breaks non-expansiveness, use n-equality instead.
Some work on the sealed case - it still does not work, but it gives an idea about where the proof fails.

\begin{lemma}
  \label{lem:codereg-not-read-write}
  If $n > 0$, $\dom(\code) \subseteq \ta$, $\gc = (\ta,\stkb)$, $\pwheap(r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$ and $a \in \dom(\code)$ and $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$ and $\sigrets \neq \emptyset$, then
  \begin{itemize}
  \item $\npair{\{a\}} \not\in \readCond{\normal,W}$
    % \item $\npair{\{a\}} \not\in \writeCond{\normal,W}$
    % It seems unnecessary to show the part about the write condition as all non-no-perm permissions have read.
  \end{itemize}
\end{lemma}
\begin{proof}
  For the sake of contradiction assume $\npair{\{a\}} \in \readCond{\normal,W}$.
  Then there exists $S \subseteq \addressable{\lin, \pwheap}$ and $R : S \fun
  \powerset{\nats}$ such that
  \begin{itemize}
  \item $\biguplus_{r\in S} R(r) \supseteq A$
  \item $\forall r \in S \ldotp \pwheap(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$
  \end{itemize}
  We claim that $r_\code \in S$\lau{TODO: show this claim}.
  If this is indeed the case, then we have $\pwheap(r_\code).H \nsubeq \stdreg{\dom(\code),\gc}{\pur}.H$ (we must have $R(r_\code) = \dom(\code)$ as the two regions couldn't be $\nequal$ otherwise).
  This means that for all $a \in \dom(\code)$ and $n' < n$ it must be the case that $\npair[n']{(\code(a),\code(a))} \in \lrv(W_a)$ for all $W_a$ that are compatible w.r.t.
  $\oplus$ and combine to be $W$.
  We know that $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$ and $\pwheap(r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$ from which we can deduce $\npair{(\code,\code)} \in H^\mathrm{code} \; \sigrets \; \sigcloss \; \code \; (\ta,\_) \; \xi^{-1}(W_\code)$ which in particular gives us $\sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \code$.
  This in turns entails that for $\sigma \in \sigrets$ there exists some $a' \in \dom(\code)$ such that $\code(a') = \seal{\sigma_\aaddr,\sigma_\baddr,\sigma_\eaddr}$ and $\sigma \in [\sigma_\baddr,\sigma_\eaddr]$.
  This means that for such a $\sigma$ and $a'$, it must be that case that
  $\npair[n']{(\seal{\sigma_\aaddr,\sigma_\baddr,\sigma_\eaddr},\seal{\sigma_\aaddr,\sigma_\baddr,\sigma_\eaddr})}
  \in \lrv(W_{a'})$ which gives us
  $\codereg{\sigrets,\sigcloss,\code,\gc}.H_\sigma  \; \sigma \nequal \lrv$
  contradicting Lemma~\ref{lem:codereg-Hsigma-not-lrv}.

@@

  \item If $w = \sealed{\sigma,\vsc}$ and $\sigma \not\in (\sigrets\cup \sigcloss)$ then $\vsc$ is reasonable:
    TODO

>>>>

\begin{lemma}
  \label{lem:codereg-not-read-write}
  If $n > 0$, $\dom(\code) \subseteq \ta$, $\gc = (\ta,\stkb)$, $\pwheap(r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$ and $a \in \dom(\code)$ and $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$ and $\sigrets \neq \emptyset$, then
  \begin{itemize}
  \item $\npair{\{a\}} \not\in \readCond{\normal,W}$
    % \item $\npair{\{a\}} \not\in \writeCond{\normal,W}$
    % It seems unnecessary to show the part about the write condition as all non-no-perm permissions have read.
  \end{itemize}
\end{lemma}
\begin{proof}
  For the sake of contradiction assume $\npair{\{a\}} \in \readCond{\normal,W}$.
  Then there exists $S \subseteq \addressable{\lin, \pwheap}$ and $R : S \fun
  \powerset{\nats}$ such that
  \begin{itemize}
  \item $\biguplus_{r\in S} R(r) \supseteq A$
  \item $\forall r \in S \ldotp \pwheap(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$
  \end{itemize}
  We claim that $r_\code \in S$.
  If this is indeed the case, then we have $\pwheap(r_\code).H \nsubeq \stdreg{\dom(\code),\gc}{\pur}.H$ (we must have $R(r_\code) = \dom(\code)$ as the two regions couldn't be $\nequal$ otherwise).
  This means that for all $a \in \dom(\code)$ and $n' < n$ it must be the case that $\npair[n']{(\code(a),\code(a))} \in \lrv(W_a)$ for all $W_a$ that are compatible w.r.t.
  $\oplus$ and combine to be $W$.
  We know that $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$ and $\pwheap(r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$ from which we can deduce $\npair{(\code,\code)} \in H^\mathrm{code} \; \sigrets \; \sigcloss \; \code \; (\ta,\_) \; \xi^{-1}(W_\code)$ which in particular gives us $\sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \code$.
  This in turns entails that for $\sigma \in \sigrets$ there exists some $a' \in \dom(\code)$ such that $\code(a') = \seal{\sigma_\aaddr,\sigma_\baddr,\sigma_\eaddr}$ and $\sigma \in [\sigma_\baddr,\sigma_\eaddr]$.
  This means that for such a $\sigma$ and $a'$, it must be that case that
  $\npair[n']{(\seal{\sigma_\aaddr,\sigma_\baddr,\sigma_\eaddr},\seal{\sigma_\aaddr,\sigma_\baddr,\sigma_\eaddr})}
  \in \lrv(W_{a'})$ which gives us
  $\codereg{\sigrets,\sigcloss,\code,\gc}.H_\sigma  \; \sigma \nequal \lrv$
  contradicting Lemma~\ref{lem:codereg-Hsigma-not-lrv}.

@@

  \item If $w = \sealed{\sigma,\vsc}$ and $\sigma \not\in (\sigrets\cup \sigcloss)$ then $\vsc$ is reasonable: By $\npair{(w,\_)} \in \lrv(W_w)$, we get some region $r \in \dom(\pwheap)$ and a set of return seals, a set of closure seals and a code memory: $\sigrets',\sigcloss',\mscode'$ such that $\pwheap(r) = (\pure,\_,H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode' \; \gc)$ and $\npair[n']{(\sealed{\sigma,\vsc},\_)} \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode' \; \gc \; \sigma \; \xi^{-1}(W) \text{ for all $n' < n$}$.

    It also follows that $\sigrets \uplus \sigcloss \# \sigrets' \uplus \sigcloss'$.

    This gives us three cases for $\vsc$.
    The two first cases $\vsc = \retptrd(\_,\_)$ and $\vsc = \retptrc(\_,\_,\_)$ are easily discharged as the reasonability definition puts no requirements on return pointers.
    For the final case, $\sigma \in \sigcloss$ and either
    \begin{itemize}
    \item $\dom(\code') \mathrel{\#} \ta \tand \npair[n']{(\vsc,\vsc')} \in \lrv \;
      \xi(\hat{W})$; or
    \item $\dom(\code') \subseteq \ta \tand \npair[n']{(\vsc,\vsc')} \in \lrvtrusted \; \xi(\hat{W})$
    \end{itemize}
    \lau{At this point, it seems like should have done the proof by induction,
      but this would not be possible with the $n>0$ assumption (at least not if
      we want to use the IH). In the latter case, it is probably difficult to
      show that the something is in the trusted value-relation. If we assume
      $\ta = \dom(\code)$, then this may be discharged by contradiction (we may
      somewhere need to assume that $\ta \neq \emptyset$).}
    TODO
